Seafood globalization preliminary results

### 2022-08-19 Methods.Rmd
add ms figures file

To convert reported bilateral trade of seafood products to species trade flows, we first identify the mix of species going into each trade code. To do this, we first must reweight $X$ so it represents the proportion of each species in a given code rather than the proportion of production of a species going into each product form. To do this, we take each country's estimated $X$, multiply by  production, and divide by the column sums.

Next, we calculate the proportion of exports sourced from national production, imported and processed products, and from an unknown source (i.e., the error term). Since the mix of these sources cannot be derived from the mass balance equation alone, we calculate a range for the sourcing following Asche et al. (2022). To calculate the maximum exports from domestic production,  We apply the national reweighted $X$ to the exports from national production and the reweighted $X$ of trade partners (weighted based on import volume of each trade code) to import-sourced exports. Since the exports are of an unknown origin, we assign the most resolved common taxonomic name for the species falling within the code to the exports derived from the error term. [ADD EXAMPLE]

>>>>

###______________________________________________________________________________________###
Old text
To convert reported bilateral trade of seafood products to species trade flows, we first identify the mix of species going into each trade code. To do this, we first must reweight $X$ so it represents the proportion of each species in a given code rather than the proportion of production of a species going into each product form. To do this, we take each country's estimated $X$, multiply by  production, and divide by the column sums.

Next, we calculate the proportion of exports sourced from national production, imported and processed products, and from an unknown source (i.e., the error term). Since the mix of these sources cannot be derived from the mass balance equation alone, we calculate a range for the sourcing following Asche et al. (2022). To calculate the maximum exports from domestic production,  We apply the national reweighted $X$ to the exports from national production and the reweighted $X$ of trade partners (weighted based on import volume of each trade code) to import-sourced exports. Since the exports are of an unknown origin, we assign the most resolved common taxonomic name for the species falling within the code to the exports derived from the error term. 
###______________________________________________________________________________________###

To convert bilateral trade data expressed as commodities into species flows, we must trace flows back to their source country to link the commodities with the appropriate species mix. To do this, we draw from multi-regional input-output methods and first construct a flow matrix $F$, with sectors representing all country-commodity combinations and the origin ("from") sector on the row and destination ("to") sector on the column. To construct $F$, we multiply the estimated conversion of products for each country $i$ ($W_i$) element wise by the vector of imports by country-commodity combination, expressed as live weight equivalents. This then represents the bilateral flow of product entering each country and remaining in its current form and being processed into a new form according to the appropriate estimated national $W$ matrix.

Our final demand vector is comprised of domestic production of each commodity ($X_i p_i$) plus imports of each commodity expressed as the final product form ($W_i g$) plus the estimated error export quantity ($\epsilon$).

### 2022-08-19 prelim_results.Rmd
add ms figures file

---
title: "Seafood globalization preliminary results"
author: "Jessica Gephart"
output: html_document
---

@@

library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)

@@

# Pull all ARTIS and production data
artis <- dbGetQuery(con, 
"SELECT * FROM snet 
WHERE (snet_est = \'mid\') AND
((\"year\" <= 2003 AND hs_version = \'HS96\') OR
((\"year\" > 2003 AND \"year\" <= 2009) AND hs_version = \'HS02\') OR
((\"year\" > 2009 AND \"year\" <= 2012) AND hs_version = \'HS07\') OR
((\"year\" > 2012 AND \"year\" <= 2020) AND hs_version = \'HS12\'))")

artis <- artis %>%
  select(-record_id, -snet_est)

prod <- dbGetQuery(con, "SELECT * FROM production")
prod <- prod %>%
  select(-record_id)

@@

# Trend in global seafood trade

@@

total_1996 <- round(sum(artis %>% filter(year == 1996) %>% pull(live_weight_t))/1000000, 1)
total_2019 <- round(sum(artis %>% filter(year == 2019) %>% pull(live_weight_t))/1000000, 1)
```

@@

@@

## Number of exporters by source
kable(artis %>% 
        select(year, exporter_iso3c, method) %>%
        distinct() %>%
        group_by(year, method) %>%
        tally() %>%
        select(year, method, n) %>% 
        pivot_wider(names_from = method, values_from = n),
      caption = "Number of exporters by production source")

@@

```{r regional_bilateral_trends}
artis_region <- artis %>%
  mutate(importer_region = countrycode(importer_iso3c, origin = "iso3c", destination = "region"),
         exporter_region = countrycode(exporter_iso3c, origin = "iso3c", destination = "region")) %>%
  group_by(year, exporter_region, importer_region) %>%
  summarise(live_weight_t = sum(live_weight_t))

artis_region %>%
  filter(!is.na(exporter_region), !is.na(importer_region)) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000)) +
  geom_line() +
  labs(x = "", y = "Exports (million t)") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_grid(exporter_region~importer_region, scales = "free",
             labeller = label_wrap_gen(width = 5))

@@

```{r top_bilateral_flows}
top_flows_1 <- artis %>%
  filter(year %in% 1996:2000) %>% 
  group_by(exporter_iso3c, importer_iso3c) %>%
  summarise(live_weight_t = sum(live_weight_t)/5) %>%
  arrange(desc(live_weight_t)) %>%
  ungroup() %>%
  slice_max(n = 25, order_by = live_weight_t) %>%
  mutate(exporter_to_importer = paste(
    countrycode(exporter_iso3c, origin = "iso3c", destination = "country.name"), 
    "to",
    countrycode(importer_iso3c, origin = "iso3c", destination = "country.name"),
    sep = " ")) %>%
  mutate(exporter_to_importer = fct_reorder(exporter_to_importer, live_weight_t)) %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter_to_importer)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 25 bilateral \nflows (1996-2000)", x = "Average trade (million t)", y = "") +
  theme_bw()

@@

@@

## Percent of exports by source
kable(artis %>% 
        group_by(year, dom_source) %>%
        summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
        mutate(percent = round(100*live_weight_t/sum(live_weight_t), 1)) %>%
        select(year, dom_source, percent) %>% 
        pivot_wider(names_from = dom_source, values_from = percent),
      caption = "Percent of exports by export source")
```

@@

```{r exports_percent_by_species}
prod_1 <- artis %>%
  filter(dom_source == "domestic export", 
         year %in% 1996:2000) %>%
  select(exporter_iso3c, sciname, production_t) %>%
  distinct() %>%
  group_by(sciname) %>%
  summarise(production_t = sum(production_t, na.rm = TRUE))

@@

# Percent of supply by source for select countries
supply %>% 
  filter(iso3c %in% select_countries) %>%
  mutate(supply_no_error = case_when(supply_no_error < 0 ~ 0,
                                     TRUE ~ supply_no_error)) %>%
  group_by(iso3c, year) %>%
  summarise(supply_domestic = 100*sum(supply_domestic)/sum(supply_no_error),
            supply_foreign = 100*sum(supply_foreign)/sum(supply_no_error)) %>%
  ggplot() +
  geom_line(aes(x = year, y = supply_domestic), color = "#1B708F") +
  geom_line(aes(x = year, y = supply_foreign), color = "#E24027") +
  labs(x = "", y = "Percent of supply (blue = domestic; red = domestic)") +
  facet_wrap(~iso3c) +
  theme_bw()

supply %>% 
  mutate(region = countrycode(iso3c, origin = "iso3c", destination = "region")) %>%
  mutate(supply_no_error = case_when(supply_no_error < 0 ~ 0,
                                     TRUE ~ supply_no_error)) %>%
  group_by(region, year) %>%
  summarise(supply_domestic = 100*sum(supply_domestic)/sum(supply_no_error),
            supply_foreign = 100*sum(supply_foreign)/sum(supply_no_error)) %>%
  filter(region != "NA") %>%
  ggplot() +
  geom_line(aes(x = year, y = supply_domestic), color = "#1B708F") +
  geom_line(aes(x = year, y = supply_foreign), color = "#E24027") +
  labs(x = "", y = "Percent of supply (blue = domestic; red = domestic)") +
  facet_wrap(~region) +
  theme_bw()

@@

supply_species %>% 
  group_by(sciname, CommonName) %>% 
  mutate(total_production_t = sum(production_t)) %>%
  ungroup() %>%
  slice_max(n = 16*length(unique(supply_species$year)), order_by = total_production_t) %>%
  ggplot() +
  geom_line(aes(x = year, y = percent_domestic), color = "#1B708F") + 
  geom_line(aes(x = year, y = percent_foreign), color = "#E24027") +
  labs(x = "", y = "Percent of supply (blue = domestic; red = domestic)") +
  facet_wrap(~CommonName) +
  theme_bw()

@@

```{r explore_country_error}
# Plot time series of species with largest volume error exports
supply %>%
  group_by(year, iso3c) %>%
  summarise(error_export = sum(error_export, na.rm = TRUE), 
            domestic_export = sum(domestic_export, na.rm = TRUE),
            foreign_export = sum(foreign_export, na.rm = TRUE),
            error_percent = 100*sum(error_export, na.rm = TRUE)/(sum(domestic_export, na.rm = TRUE) + 
                                                     sum(foreign_export, na.rm = TRUE) + 
                                                     sum(error_export, na.rm = TRUE))) %>%
  group_by(iso3c) %>%
  mutate(total_error = sum(error_export)) %>%
  ungroup() %>%
  slice_max(n = 12*length(unique(supply$year)), order_by = total_error) %>%
  ggplot(aes(x = year, y = error_percent)) +
  geom_line() +
  labs(x = "", y = "Percent exports from unknown source") +
  facet_wrap(~iso3c) +
  theme_bw()

@@

```{r explore_species_error}
# Plot time series of species with largest volume error exports
supply %>%
  group_by(year, sciname, CommonName) %>%
  summarise(error_export = sum(error_export, na.rm = TRUE), 
            domestic_export = sum(domestic_export, na.rm = TRUE),
            foreign_export = sum(foreign_export, na.rm = TRUE),
            error_percent = 100*sum(error_export, na.rm = TRUE)/(sum(domestic_export, na.rm = TRUE) + 
                                                     sum(foreign_export, na.rm = TRUE) + 
                                                     sum(error_export, na.rm = TRUE))) %>%
  # Remove groupings only used by error 
  filter(!(sciname %in% c("animalia", "actinopteri"))) %>%
  group_by(sciname, CommonName) %>%
  mutate(total_error = sum(error_export)) %>%
  ungroup() %>%
  slice_max(n = 12*length(unique(supply$year)), order_by = total_error) %>%
  ggplot(aes(x = year, y = error_percent)) +
  geom_line() +
  labs(x = "", y = "Percent exports from unknown source") +
  facet_wrap(~CommonName) +
  theme_bw()

>>>>

---
title: "Seafood globalization preliminary results"
author: "Jessica Gephart"
output: 
  pdf_document
---

@@

library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)
library(broom)
library(exploreARTIS)

@@

# Pull all ARTIS and production data
artis <- dbGetQuery(con, "SELECT * FROM snet")

artis <- artis %>%
  select(-record_id) %>%
  # Remove 2020 for now
  filter(year < 2020)

prod <- dbGetQuery(con, "SELECT * FROM production")
prod <- prod %>%
  select(-record_id) %>%
  # Remove 2020 for now
  filter(year < 2020)

@@

# Trends in global seafood trade

@@

artis_fmfo_ts <- artis %>% 
  mutate(food_or_fmfo = case_when(
    hs6 == "230120" ~ "fishmeal",
    hs6 != "230120" ~ "nonfishmeal"
  )) %>%
  group_by(year, food_or_fmfo) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE))

artis_fmfo_ts %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = food_or_fmfo)) +
  geom_area() +
  scale_fill_manual(values = method_colors) +
  labs(x = "", y = "Seafood exports (million t, live weight)", fill = "") +
  theme_minimal()

artis_fmfo_ts_summary <- artis_fmfo_ts %>%
  pivot_wider(names_from = food_or_fmfo, values_from = live_weight_t) %>%
  mutate(percent_fishmeal = 100*fishmeal/(fishmeal+nonfishmeal))

total_1996 <- round(sum(artis %>% filter(year == 1996) %>% pull(live_weight_t))/1000000, 1)
total_2019 <- round(sum(artis %>% filter(year == 2019) %>% pull(live_weight_t))/1000000, 1)

total_capture_1996 <- round(sum(artis %>% filter(year == 1996, method == "capture") %>% pull(live_weight_t))/1000000, 1)
total_capture_2019 <- round(sum(artis %>% filter(year == 2019, method == "capture") %>% pull(live_weight_t))/1000000, 1)

total_aquaculture_1996 <- round(sum(artis %>% filter(year == 1996, method == "aquaculture") %>% pull(live_weight_t))/1000000, 1)
total_aquaculture_2019 <- round(sum(artis %>% filter(year == 2019, method == "aquaculture") %>% pull(live_weight_t))/1000000, 1)

@@

Global capture fishery trade increased from `r total_capture_1996` million t (live weight) in 1996 to `r total_capture_2019` million t (live weight) in 2019, representing a `r round(100*((total_capture_2019-total_capture_1996)/total_capture_1996),0)`% increase over that period. In 1996, capture fishery trade represented `r round(100*total_capture_1996/total_1996)`% of all seafood exports and by 2019 capture fishery exports represented `r round(100*total_capture_2019/total_2019)`% of all seafood exports.

Global aquaculture fishery trade increased from `r total_aquaculture_1996` million t (live weight) in 1996 to `r total_aquaculture_2019` million t (live weight) in 2019, representing a `r round(100*((total_aquaculture_2019-total_aquaculture_1996)/total_aquaculture_1996),0)`% increase over that period. In 1996, aquaculture fishery trade represented `r round(100*total_aquaculture_1996/total_1996)`% of all seafood exports and by 2019 capture fishery exports represented `r round(100*total_aquaculture_2019/total_2019)`% of all seafood exports.

@@

## Number of exporters by source
kable(artis %>% 
        filter(live_weight_t>10) %>%
        select(year, exporter_iso3c, method) %>%
        distinct() %>%
        group_by(year, method) %>%
        tally() %>%
        select(year, method, n) %>% 
        pivot_wider(names_from = method, values_from = n),
      caption = "Number of exporters by production source")

@@

```{r capture_aqua_sankey, eval = FALSE}
artis %>% 
  filter(method == "capture", year %in% 2015:2019) %>% 
  plot_sankey(prop_flow_cutoff = 0.03)

artis %>% 
  filter(method == "aquaculture", year %in% 2015:2019) %>% 
  plot_sankey(prop_flow_cutoff = 0.03)
```

```{r regional_bilateral_trends}
artis_region <- artis %>%
  mutate(importer_region = countrycode(importer_iso3c, origin = "iso3c", destination = "region"),
         exporter_region = countrycode(exporter_iso3c, origin = "iso3c", destination = "region")) %>%
  filter(!is.na(importer_region), !is.na(exporter_region)) %>%
  group_by(year, exporter_region, importer_region) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(exporter_importer = paste(exporter_region, " to ", importer_region, sep = ""))

region_slopes <- artis_region %>%
  split(.$exporter_importer) %>% 
  map(~lm(live_weight_t~year, data = .x)) %>% 
  map_df(broom::tidy, .id = 'exporter_importer') %>%
  filter(term == 'year') %>%
  select(exporter_importer, "slope" = "estimate")

artis_region <- artis_region %>%
  left_join(region_slopes, by = "exporter_importer")
```

```{r region_trend_lollipop, fig.height=7, fig.width=5}
region_slopes %>%
  mutate(exporter_importer = fct_reorder(exporter_importer, slope)) %>%
  ggplot(aes(x = slope/1000, y = exporter_importer, color = slope, fill = slope)) +
  geom_segment(aes(xend = 0, yend = exporter_importer)) +
  geom_point() +
  scale_color_gradient2(low = "#E24027", mid = "grey70", high = "#1B708F") +
  scale_fill_gradient2(low = "#E24027", mid = "grey70", high = "#1B708F") +
  labs(y = "", x = "Ave. annual change in export (1000 t live weight)") +
  theme_bw() +
  theme(legend.position = "blank")

@@

```{r region_trend_matrix, fig.height=7, fig.width=7}
artis_region %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, color = slope/1000)) +
  geom_line() +
  scale_color_gradient2(low = "#E24027", mid = "grey70", high = "#1B708F") +
  labs(x = "", y = "Exports (million t)", color = "Ave. annual change in export \n(1000 t live weight)") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
        legend.position = "bottom") +
  facet_grid(rows = vars(exporter_region), cols = vars(importer_region), scales = "free",
             labeller = label_wrap_gen(width = 5))

```{r region_trend_heatmap}
region_slopes %>%
  separate(exporter_importer, into = c("exporter", "importer"), sep = " to ") %>% 
  ggplot(aes(x = exporter, y = importer, fill = slope/1000)) +
  geom_tile() +
  scale_fill_gradient2(low = "#E24027", mid = "grey90", high = "#1B708F") +
  labs(x = "Exporting region", y = "Importing region", fill = "Ave. annual change in export \n(1000 t live weight)") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
        legend.position = "bottom")
```

```{r summarize_region_slopes}
kable(region_slopes %>%
  separate(exporter_importer, into = c("exporter", "importer"), sep = " to ") %>% 
  mutate(slope_dir = case_when(
    slope > 0 ~ 1, 
    slope < 0 ~ 0
  )) %>% 
  group_by(exporter) %>%
  summarise(total_increases = sum(slope_dir)) %>%
  arrange(desc(total_increases)), col.names = c("Exporting region", "Number of increases"))

```{r econ_group_trends}
# LCD countries according to UN (https://www.un.org/development/desa/dpad/least-developed-country-category/ldcs-at-a-glance.html)
LCD_countries <- c("Afghanistan", "Angola", "Bangladesh", "Benin", "Bhutan", "Burkina Faso", "Burundi", "Cambodia", "Central African Republic", "Chad", "Comoros", "Democratic Republic of the Congo", "Djibouti", "Eritrea", "Ethiopia", "Gambia", "Guinea", "Guinea-Bissau", "Haiti", "Kiribati", "Lao People’s Dem. Republic", "Lesotho", "Liberia", "Madagascar", "Malawi", "Mali", "Mauritania", "Mozambique", "Myanmar", "Nepal", "Niger", "Rwanda", "Sao Tome and Principe", "Senegal", "Sierra Leone", "Solomon Islands", "Somalia", "South Sudan", "Sudan", "Timor-Leste", "Togo", "Tuvalu", "Uganda", "United Republic of Tanzania", "Yemen", "Zambia")

LCD_countries <- countrycode(LCD_countries, origin = "country.name", destination = "iso3c")

artis_lcd <- artis %>%
  mutate(
    importer_region = case_when(
    (importer_iso3c %in% LCD_countries) ~ "LCD",
    !(importer_iso3c %in% LCD_countries) ~ "non-LCD"),
     exporter_region = case_when(
    (exporter_iso3c %in% LCD_countries) ~ "LCD",
    !(exporter_iso3c %in% LCD_countries) ~ "non-LCD")) %>%
  group_by(year, exporter_region, importer_region, method) %>%
  summarise(live_weight_t = sum(live_weight_t))

artis_lcd %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = method)) +
  geom_area() +
  scale_fill_manual(values = method_colors) +
  labs(x = "", y = "Exports (million t)") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_grid(rows = vars(exporter_region), cols = vars(importer_region))

artis_lcd %>% 
  group_by(importer_region, year, method) %>%
  summarise(total_imports = sum(live_weight_t)) %>%
  rename("region" = "importer_region") %>%
  left_join(artis_lcd %>% 
              group_by(exporter_region, year, method) %>%
              summarise(total_exports = sum(live_weight_t)) %>%
              rename("region" = "exporter_region"),
            by = c("year", "region", "method")) %>%
  filter(region == "LCD") %>%
  mutate(net_export = total_exports - total_imports) %>%
  ggplot(aes(x = year, y = net_export, color = method)) +
  scale_color_manual(values = method_colors) +
  geom_line() +
  labs(x = "", y = "Net export (t, live weight)") +
  ylim(c(0, 3100000)) +
  theme_bw()
```

```{r top_bilateral_flows, fig.height=4, fig.width=7}
top_flows_1 <- artis %>%
  filter(year %in% 1996:2000) %>% 
  group_by(exporter_iso3c, importer_iso3c) %>%
  summarise(live_weight_t = sum(live_weight_t)/5) %>%
  arrange(desc(live_weight_t)) %>%
  ungroup() %>%
  slice_max(n = 25, order_by = live_weight_t) %>%
  mutate(exporter_to_importer = paste(
    countrycode(exporter_iso3c, origin = "iso3c", destination = "country.name"), 
    "to",
    countrycode(importer_iso3c, origin = "iso3c", destination = "country.name"),
    sep = " ")) %>%
  mutate(exporter_to_importer = fct_reorder(exporter_to_importer, live_weight_t)) %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter_to_importer)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 25 bilateral \nflows (1996-2000)", x = "Average trade (million t)", y = "") +
  theme_bw()

@@

```{r country_bilateral_trends, eval=FALSE}

country_slopes <- artis %>%
  mutate(exporter_importer = paste(exporter_iso3c, " to ", importer_iso3c, sep = "")) %>%
  split(.$exporter_importer) %>% 
  map(~lm(live_weight_t~year, data = .x)) %>% 
  map_df(broom::tidy, .id = 'exporter_importer') %>%
  filter(term == 'year') %>%
  select(exporter_importer, "slope" = "estimate")

@@

## Percent of exports by source
kable(artis %>% 
        group_by(year, dom_source) %>%
        summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
        mutate(percent = round(100*live_weight_t/sum(live_weight_t), 1)) %>%
        select(year, dom_source, percent) %>% 
        pivot_wider(names_from = dom_source, values_from = percent),
      caption = "Percent of exports by export source")

total_domestic_1996 <- round(sum(artis %>% filter(year == 1996, dom_source == "domestic export") %>% pull(live_weight_t))/1000000, 1)
total_domestic_2019 <- round(sum(artis %>% filter(year == 2019, dom_source == "domestic export") %>% pull(live_weight_t))/1000000, 1)

total_foreign_1996 <- round(sum(artis %>% filter(year == 1996, dom_source == "foreign export") %>% pull(live_weight_t))/1000000, 1)
total_foreign_2019 <- round(sum(artis %>% filter(year == 2019, dom_source == "foreign export") %>% pull(live_weight_t))/1000000, 1)

Global domestic exports increased from `r total_domestic_1996` million t (live weight) in 1996 to `r total_domestic_2019` million t (live weight) in 2019, representing a `r round(100*((total_domestic_2019-total_domestic_1996)/total_domestic_1996),0)`% increase over that period. In 1996, domestic exports represented `r round(100*total_domestic_1996/total_1996)`% of all  exports and by 2019 domestic exports represented `r round(100*total_domestic_2019/total_2019)`% of all seafood exports.

Global foreign (i.e., imported and re-exported) exports increased from `r total_foreign_1996` million t (live weight) in 1996 to `r total_foreign_2019` million t (live weight) in 2019, representing a `r round(100*((total_foreign_2019-total_foreign_1996)/total_foreign_1996),0)`% increase over that period. In 1996, foreign exports represented `r round(100*total_foreign_1996/total_1996)`% of all  exports and by 2019 foreign exports represented `r round(100*total_foreign_2019/total_2019)`% of all seafood exports.

@@

```{r exports_percent_by_species, fig.width=5, fig.height=7}
prod_1 <- artis %>%
  filter(dom_source == "domestic export", 
         year %in% 1996:2000) %>%
  select(exporter_iso3c, sciname, production_t) %>%
  distinct() %>%
  group_by(sciname) %>%
  summarise(production_t = sum(production_t, na.rm = TRUE))

@@

# Percent of supply by source for select countries
supply %>% 
  filter(iso3c %in% select_countries) %>%
  mutate(supply_no_error = case_when(supply_no_error < 0 ~ 0,
                                     TRUE ~ supply_no_error)) %>%
  group_by(iso3c, year) %>%
  summarise(supply_domestic = 100*sum(supply_domestic)/sum(supply_no_error),
            supply_foreign = 100*sum(supply_foreign)/sum(supply_no_error)) %>%
  ggplot() +
  geom_line(aes(x = year, y = supply_domestic), color = "#1B708F") +
  geom_line(aes(x = year, y = supply_foreign), color = "#E24027") +
  labs(x = "", y = "Percent of supply (blue = domestic; red = foreign)") +
  facet_wrap(~iso3c) +
  theme_bw()
```

```{r supply_source_by_region}

supply %>% 
  mutate(region = countrycode(iso3c, origin = "iso3c", destination = "region")) %>%
  mutate(supply_no_error = case_when(supply_no_error < 0 ~ 0,
                                     TRUE ~ supply_no_error)) %>%
  group_by(region, year) %>%
  summarise(supply_domestic = 100*sum(supply_domestic)/sum(supply_no_error),
            supply_foreign = 100*sum(supply_foreign)/sum(supply_no_error)) %>%
  filter(region != "NA") %>%
  ggplot() +
  geom_line(aes(x = year, y = supply_domestic), color = "#1B708F") +
  geom_line(aes(x = year, y = supply_foreign), color = "#E24027") +
  labs(x = "", y = "Percent of supply (blue = domestic; red = foreign)") +
  facet_wrap(~region) +
  theme_bw()

@@

supply_species %>% 
  group_by(sciname, CommonName) %>% 
  mutate(total_production_t = sum(production_t)) %>%
  ungroup() %>%
  slice_max(n = 16*length(unique(supply_species$year)), order_by = total_production_t) %>%
  ggplot() +
  geom_line(aes(x = year, y = percent_domestic), color = "#1B708F") + 
  geom_line(aes(x = year, y = percent_foreign), color = "#E24027") +
  labs(x = "", y = "Percent of supply (blue = domestic; red = foreign)") +
  facet_wrap(~CommonName) +
  theme_bw()

@@

```{r explore_country_error, eval=FALSE}
# Plot time series of species with largest volume error exports
supply %>%
  group_by(year, iso3c) %>%
  summarise(error_export = sum(error_export, na.rm = TRUE), 
            domestic_export = sum(domestic_export, na.rm = TRUE),
            foreign_export = sum(foreign_export, na.rm = TRUE),
            error_percent = 100*sum(error_export, na.rm = TRUE)/(sum(domestic_export, na.rm = TRUE) + 
                                                     sum(foreign_export, na.rm = TRUE) + 
                                                     sum(error_export, na.rm = TRUE))) %>%
  group_by(iso3c) %>%
  mutate(total_error = sum(error_export)) %>%
  ungroup() %>%
  slice_max(n = 12*length(unique(supply$year)), order_by = total_error) %>%
  ggplot(aes(x = year, y = error_percent)) +
  geom_line() +
  labs(x = "", y = "Percent exports from unknown source") +
  facet_wrap(~iso3c) +
  theme_bw()

@@

```{r explore_species_error, eval=FALSE}
# Plot time series of species with largest volume error exports
supply %>%
  group_by(year, sciname, CommonName) %>%
  summarise(error_export = sum(error_export, na.rm = TRUE), 
            domestic_export = sum(domestic_export, na.rm = TRUE),
            foreign_export = sum(foreign_export, na.rm = TRUE),
            error_percent = 100*sum(error_export, na.rm = TRUE)/(sum(domestic_export, na.rm = TRUE) + 
                                                     sum(foreign_export, na.rm = TRUE) + 
                                                     sum(error_export, na.rm = TRUE))) %>%
  # Remove groupings only used by error 
  filter(!(sciname %in% c("animalia", "actinopteri"))) %>%
  group_by(sciname, CommonName) %>%
  mutate(total_error = sum(error_export)) %>%
  ungroup() %>%
  slice_max(n = 12*length(unique(supply$year)), order_by = total_error) %>%
  ggplot(aes(x = year, y = error_percent)) +
  geom_line() +
  labs(x = "", y = "Percent exports from unknown source") +
  facet_wrap(~CommonName) +
  theme_bw()
